title: "Assignment4"
author: "khanhthuong2804"
date: "17/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
The package Assignment4 is mainly used for present summary and plots of public yearly data with CSV files  
Firstly load in the necessary packages 
```{r load-in,message=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(Assignment4)
```


# `fars_read` function
to specify the name of CSV file containing data of certain year if you know one
```{r path}
accident <- fars_read("accident_2015.csv.bz2")
accident %>% slice(1:5)
```
Practically, this function serves an intermediate function to `fars_read_years` and `fars_map_state` functions.

#  `fars_read_years` function
```{r read_years}
years <- c(2013,2014,2015)
fars_read_years(years)[[1]]
```

# `fars_summarize` function 
Initiate the years vector and input it in `fars_summarize`, the result is preseted in a tibble 
```{r initiate, eval=FALSE}
fars_summarize_years(years)
```
```{r run_summarize, echo=FALSE}
fars_summarize_years(c(2013,2014,2015))
```


